\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french]{babel}
\usepackage{lmodern}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amsfonts,mathrsfs,amssymb}
\usepackage{numprint}
\usepackage{amsthm}
\usepackage{pstricks,pst-eucl,pstricks-add,pst-math,pst-xkey,pst-tree}
\usepackage{subfig}
\usepackage{enumitem}
\usepackage{stmaryrd}
\usepackage[all]{genealogytree}
\usepackage{tikz}
\usepackage[backend=biber, sorting=none]{biblatex}
\addbibresource{ref.bib}


\usepackage{listings}

\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{deepred}{rgb}{0.6,0,0}

\lstdefinelanguage{scala}{
  morekeywords={abstract,case,catch,class,def,%
    do,else,extends,false,final,finally,%
    for,if,implicit,import,match,mixin,%
    new,null,object,override,package,%
    private,protected,requires,return,sealed,%
    super,this,throw,trait,true,try,%
    type,val,var,while,with,yield},
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[n]{/*}{*/},
  morestring=[b]",
  morestring=[b]',
  morestring=[b]"""
}


\lstset{frame=tb,
  language=scala,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  texcl=true,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{orange},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  emph={val},
  emphstyle=\color{deepred},
  morekeywords={Seq},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}


\usepackage{framed}
\setlength{\parindent}{0pt}
\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparsep}{0cm}
\setlength{\parskip}{0cm}
%\setlength{\topskip}{0cm}
\renewcommand{\headrulewidth}{0.5pt}
%\renewcommand{\footrulewidth}{0.5pt}
\definecolor{fond}{gray}{0.95}
\newenvironment{cadrecode}{%
  \def\FrameCommand{{\color[HTML]{888888}\vrule width 3pt}\colorbox{fond}}%
  \MakeFramed {\advance\hsize-\width \FrameRestore}}%
{\endMakeFramed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{geometry}
\geometry{verbose,tmargin=2.5cm,lmargin=2cm,rmargin=2cm,bmargin=2cm}
\fancyfoot[R]{\small \texttt{KTH} }
\fancyhf{}
\fancyhead[L]{\small \texttt{KTH - IDS2221} }
\fancyhead[R]{\small \texttt{2022--2023}}
\pagestyle{fancy}

\title{}
\date{}
\author{}

\usepackage{titling}
\setlength{\droptitle}{-3.5cm}

\DeclareMathOperator{\e}{e}
\newenvironment{psmallmatrix}{\left(\begin{smallmatrix}}{\end{smallmatrix}\right)}
\renewenvironment{pmatrix}{\begin{psmallmatrix}}{\end{psmallmatrix}}
\allowdisplaybreaks

\begin{document}


\thispagestyle{fancy}

\begin{center}
    {\Large\textbf{Essay on Storage}}\\
    \vspace{1em}

    {\large Oliver \bsc{Chin Wee Gui}}\\
    {\large Timothée \bsc{Ly}} \\
    {\large Erik \bsc{Kongpachith}}


\end{center}\bigskip

\section{Motivation}
Describe the motivation of the papers in your selected module. \textbf{WHY} is the addressed problem interesting and important to be solved?

\section{Contributions}
Explain the main contributions of the papers. \textbf{WHAT} are the solved problems?
You may optionally use a list of contributions. For example:
\begin{itemize}
 \item First contribution
 \item Second contribution
 \item Third contribution
\end{itemize}

\section{Solution}
Very briefly explain \textbf{HOW} the authors solve the mentioned problems.

\section{Your Opinion}
What you think about these papers? List their strong and weak points. Is the solution good? How good is the evaluation of the work? What are the disadvantages and shortcomings of the solution given by the authors? Did the authors overlook anything during the evaluation of their solution?




\end{document}
